Results

### 2021-07-23 Analysis/03_Summarise_results.Rmd
added column names

```{r}
## Loading the results
load("../Data/Processed/sim_equalizing.rda")
equalizing <- bkp
load("../Data/Processed/sim_facilitation.rda")
facilitation <- bkp
load("../Data/Processed/sim_filtering.rda")
filtering <- bkp
load("../Data/Processed/sim_competition.rda")
competition <- bkp
```

```{r}
## Loading the functions
source("../Functions/extract.table.R")
source("../Functions/plot.metric.results.R")
source("../Functions/paired.tests.R")
```

@@

  * [x]1. reworking the scaling
  * [ ]2. plotting the metrics per stressors (i.e. all metrics for each stressor).
    `TODO: re-work the plots (15 rows * 4 columns; each row is a metric and contains the lines for the 4 rarefactions; each column is a stressor)`
  * [ ]3. fitting a linear model per metric per stressor to rank models based on their r2
    > Pedro: Wonder if it makes sense to fit linear (or other) models to each trend (20, 40, 60, 80) and the higher the r2 the higher the clearer or more probable the detection of the trend?
  * [x]4. t-test (paired) of difference between each random score and the stressor
    `TODO 3+4: results table per metric`
  * [ ]5. run a psych-style pairwise comparison between each scaled metric
  * [ ]6. put the results in the context of the expectation table from the paper (Null vs process.docx)

@@

> TODO: we measure paired difference between random and stressor

```{r}
## Measuring the paired t-tests
metric_null_diff <- lapply(all_results, paired.tests)
```

>>>>

```{r}
library(knitr)
## Loading the results
load("../Data/Processed/sim_equalizing.rda")
equalizing <- bkp
load("../Data/Processed/sim_facilitation.rda")
facilitation <- bkp
load("../Data/Processed/sim_filtering.rda")
filtering <- bkp
load("../Data/Processed/sim_competition.rda")
competition <- bkp
```

```{r}
## Loading the functions
source("../Functions/extract.table.R")
source("../Functions/plot.metric.results.R")
source("../Functions/paired.tests.R")
source("../Functions/split.metric.R")
source("../Functions/fit.model.rm.R")
source("../Functions/fancy.table.R")
```

@@

  * [x]1. reworking the scaling
  * [ ]2. plotting the metrics per stressors (i.e. all metrics for each stressor).
    `TODO: re-work the plots (15 rows * 4 columns; each row is a metric and contains the lines for the 4 rarefactions; each column is a stressor)`
  * [x]3. fitting a linear model per metric per stressor to rank models based on their r2
  * [x]4. t-test (paired) of difference between each random score and the stressor
    `TODO 3+4: results table per metric`
  * [ ]5. run a psych-style pairwise comparison between each scaled metric
  * [ ]6. put the results in the context of the expectation table from the paper (Null vs process.docx)

@@

> TODO: we measure paired difference between random and stressor on the raw data
> TODO: we fitted a lm on the scaled data (scaled_metric ~ removal_level)

```{r}
## Slope and R2 for each model
model_fits <- lapply(scaled_results, fit.model.rm)
## Differences between stressor and random
null_differences <- lapply(all_results, paired.tests)

## Making the fancy tables
model_table <- fancy.table(model_fits, columns = list(c(3,4), 5))
null_table <- fancy.table(null_differences, columns = list(c(1,3), c(4, 6), c(7, 9)))
```

```{r, echo = FALSE}
kable(model_table, caption = "Results of the model scaled metric ~ removal level per stressor", align = "c")
```

```{r, echo = FALSE}
kable(null_table, caption = "Difference between the null metric and the stressed metric (raw) for each level of removal and each stressor", align = "c")
```
